---
title: "Stroke Prediction: A Comparative Classification Analysis"
author: "Niloy Paul, Mithila Chowdhury Medha, Anik Mistry"
date: "`r Sys.Date()`"
output:
  html_document: 
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
    number_sections: true
    code_folding: show
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: console
---

```{r setup, include=FALSE}

# SETUP: Global chunk options and reproducibility seed

knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5,
	fig.width = 9,
	message = TRUE,
	warning = TRUE
)
set.seed(42)  # For full reproducibility across all models and splits
```

------------------------------------------------------------------------

# Data Collection & Description

## Dataset Overview

This project uses the Healthcare Dataset of Stroke Prediction sourced
from Kaggle
(<https://www.kaggle.com/datasets/fedesoriano/stroke-prediction-dataset>).

The dataset contains health attributes that may predict
the likelihood of a stroke. It includes 5,110 observations and 12
variables (both categorical and numerical).


## Install & Load Required Libraries

```{r Load Libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

required_packages <- c(
  "tidyverse",    # Data manipulation and visualization
  "ggplot2",      # Advanced plotting
  "corrplot",     # Correlation matrix visualization
  "gridExtra",    # Multi-panel plots
  "caret",        # Unified ML training and evaluation framework
  "randomForest", # Random Forest classifier
  "xgboost",      # XGBoost classifier
  "e1071",        # Support Vector Machine
  "ROSE",         # Random Over-Sampling Examples (class imbalance)
  "knitr",        # Table formatting
  "kableExtra",   # Enhanced table styling
  "scales",       # Axis formatting in ggplot
  "pROC",         # ROC curve analysis
  "ggcorrplot"    # Correlation plot with ggplot2 style
)

# Auto-install any missing package
new_packages <- required_packages[!(required_packages %in% installed.packages()[,"Package"])]
if (length(new_packages) > 0) {
  install.packages(new_packages, repos = "https://cran.r-project.org", quiet = TRUE)
}

# Load all libraries
invisible(lapply(required_packages, library, character.only = TRUE))

cat("All libraries loaded successfully.\n")
```

## Automated Data Import (via Google Drive URL)

```{r Dataset Import, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

file_id <- "1Z28Czhbfn2zglnz9vAg0TYgmIrQeHRxE"  

gdrive_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)

temp_file <- tempfile(fileext = ".csv")

tryCatch({
  download.file(gdrive_url, destfile = temp_file, mode = "wb", quiet = TRUE)
  stroke_raw <- read.csv(temp_file, stringsAsFactors = FALSE, na.strings = c("N/A", "NA", ""))
  cat("Dataset loaded successfully from Google Drive.\n")
}, error = function(e) {
  stop("Failed to load dataset from Google Drive. Please verify the file_id and sharing permissions.\n",
       "Error: ", conditionMessage(e))
})

cat("\nFirst 5 rows of the raw dataset:\n")
head(stroke_raw, 5)
```

## Dataset Description

```{r Dataset Description, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

cat("Dataset Dimensions:", nrow(stroke_raw), "rows x", ncol(stroke_raw), "columns\n\n")

cat("Column Names and Types:\n")
str(stroke_raw)
```

# Exploratory Data Analysis (EDA)

## Summary Statistics

```{r EDA Summary, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

cat("--- Summary Statistics ---\n")
summary(stroke_raw)
```

## Missing Values Detection

```{r Missing Value, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

missing_counts <- colSums(is.na(stroke_raw))
missing_pct    <- round(missing_counts / nrow(stroke_raw) * 100, 2)

missing_df <- data.frame(
  Column          = names(missing_counts),
  Missing_Count   = missing_counts,
  Missing_Percent = missing_pct
) %>% filter(Missing_Count > 0)

if (nrow(missing_df) == 0) {
  cat("No missing values found.\n")
} else {
  kable(missing_df, row.names = FALSE,
        caption = "Missing Values per Column") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = FALSE)
}
```

## Target Variable Distribution

```{r Target Class Distribution, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

stroke_counts <- stroke_raw %>%
  count(stroke) %>%
  mutate(
    label   = ifelse(stroke == 1, "Stroke (1)", "No Stroke (0)"),
    percent = round(n / sum(n) * 100, 1)
  )

ggplot(stroke_counts, aes(x = label, y = n, fill = label)) +
  geom_bar(stat = "identity", width = 0.5, color = "white") +
  geom_text(aes(label = paste0(n, "\n(", percent, "%)")),
            vjust = -0.3, size = 4.5, fontface = "bold") +
  scale_fill_manual(values = c("#2196F3", "#F44336")) +
  labs(title = "Target Variable: Stroke Class Distribution",
       x     = "Stroke Outcome",
       y     = "Patient Count") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none") +
  ylim(0, max(stroke_counts$n) * 1.15)
```


## Distribution of Numerical Features

```{r Histogram-Numerical-Distribution, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# EDA: Histograms for numerical feature distributions

num_vars <- c("age", "avg_glucose_level", "bmi")

plots <- lapply(num_vars, function(var) {
  ggplot(stroke_raw %>% filter(!is.na(.data[[var]])),
         aes(x = .data[[var]], fill = as.factor(stroke))) +
    geom_histogram(bins = 30, alpha = 0.75, position = "identity") +
    scale_fill_manual(values = c("#42A5F5", "#EF5350"),
                      labels = c("No Stroke", "Stroke"),
                      name   = "Outcome") +
    labs(title = paste("Distribution of", var),
         x = var, y = "Count") +
    theme_minimal(base_size = 11)
})

do.call(grid.arrange, c(plots, ncol = 3))
```


## Distribution of Categorical Features

```{r Bar Chart-Categorical-Distribution, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# EDA: Bar charts for categorical feature distributions

cat_vars <- c("gender", "ever_married", "work_type", "Residence_type", "smoking_status")

cat_plots <- lapply(cat_vars, function(var) {
  ggplot(stroke_raw %>% filter(!is.na(.data[[var]])),
         aes(x = .data[[var]], fill = as.factor(stroke))) +
    geom_bar(position = "fill", alpha = 0.85) +
    scale_fill_manual(values = c("#42A5F5", "#EF5350"),
                      labels = c("No Stroke", "Stroke"),
                      name   = "Outcome") +
    scale_y_continuous(labels = percent_format()) +
    labs(title = paste("Stroke Rate by", var),
         x = var, y = "Proportion") +
    theme_minimal(base_size = 10) +
    theme(axis.text.x = element_text(angle = 30, hjust = 1))
})

do.call(grid.arrange, c(cat_plots, ncol = 2))
```

## Age vs Glucose Level: Stroke Overlay

```{r Scatter Plot, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# EDA: Scatter plot — age vs. glucose, colored by stroke

ggplot(stroke_raw %>% filter(!is.na(bmi)),
       aes(x = age, y = avg_glucose_level,
           color = as.factor(stroke), alpha = as.factor(stroke))) +
  geom_point(size = 1.8) +
  scale_color_manual(values = c("0" = "#90CAF9", "1" = "#C62828"),
                     labels = c("No Stroke", "Stroke"),
                     name   = "Outcome") +
  scale_alpha_manual(values = c("0" = 0.4, "1" = 0.9), guide = "none") +
  labs(title  = "Age vs. Average Glucose Level by Stroke Outcome",
       x      = "Age",
       y      = "Average Glucose Level") +
  theme_minimal(base_size = 13)
```

## Outlier Detection — Boxplots

```{r Outlier Detection, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# EDA: Boxplots to detect outliers in numerical variables

stroke_long <- stroke_raw %>%
  select(age, avg_glucose_level, bmi, stroke) %>%
  pivot_longer(cols = c(age, avg_glucose_level, bmi),
               names_to = "variable", values_to = "value") %>%
  filter(!is.na(value))

ggplot(stroke_long, aes(x = as.factor(stroke), y = value,
                         fill = as.factor(stroke))) +
  geom_boxplot(outlier.color = "red", outlier.alpha = 0.4,
               alpha = 0.7, width = 0.5) +
  scale_fill_manual(values = c("#42A5F5", "#EF5350"),
                    labels = c("No Stroke", "Stroke"),
                    name   = "Outcome") +
  facet_wrap(~variable, scales = "free_y") +
  labs(title = "Boxplots of Numerical Features by Stroke Outcome",
       x     = "Stroke",
       y     = "Value") +
  theme_minimal(base_size = 13)
```


## Correlation Analysis

```{r Correlation Martrix, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# EDA: Correlation matrix among numerical features

corr_data <- stroke_raw %>%
  select(age, avg_glucose_level, bmi, hypertension, heart_disease, stroke) %>%
  mutate(bmi = as.numeric(bmi)) %>%
  na.omit()

corr_matrix <- cor(corr_data)

ggcorrplot(corr_matrix,
           method    = "circle",
           type      = "lower",
           lab       = TRUE,
           lab_size  = 3.5,
           colors    = c("#2196F3", "white", "#F44336"),
           title     = "Correlation Matrix of Numerical Features",
           ggtheme   = theme_minimal())
```

# Data Preprocessing

## Step 1 — Remove Irrelevant Column

```{r preprocess-id, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Drop 'id'

stroke_df <- stroke_raw %>% select(-id)
cat("'id' column removed. Remaining columns:", ncol(stroke_df), "\n")
```

## Step 2 — Remove Rare / Uninformative Categories

```{r preprocess-gender, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Remove 'Other' gender (only 1 record) to avoid
# noise and encoding issues

cat("Gender value counts before filter:\n")
print(table(stroke_df$gender))

stroke_df <- stroke_df %>% filter(gender != "Other")
cat("\nRows after removing 'Other' gender:", nrow(stroke_df), "\n")
```

## Step 3 — Handle Missing Values

```{r preprocess-missing-values, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# BMI: Replace N/A with median
# smoking_status: Replace with 'Unknown' (meaningful category)

stroke_df$bmi <- as.numeric(stroke_df$bmi)
bmi_median <- median(stroke_df$bmi, na.rm = TRUE)
stroke_df$bmi[is.na(stroke_df$bmi)] <- bmi_median

cat("BMI missing values filled with median:", bmi_median, "\n")

stroke_df$smoking_status[is.na(stroke_df$smoking_status)] <- "Unknown"

# Confirm no missing values remain
remaining_na <- sum(is.na(stroke_df))
cat("Total missing values after imputation:", remaining_na, "\n")
```

## Step 4 — Outlier Capping (Winsorization)

```{r preprocess-outliers, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Cap outliers at 1st and 99th percentile
# Applies to: avg_glucose_level, bmi

winsorize <- function(x, lower_pct = 0.01, upper_pct = 0.99) {
  lower <- quantile(x, lower_pct, na.rm = TRUE)
  upper <- quantile(x, upper_pct, na.rm = TRUE)
  pmin(pmax(x, lower), upper)
}

stroke_df$avg_glucose_level <- winsorize(stroke_df$avg_glucose_level)
stroke_df$bmi                <- winsorize(stroke_df$bmi)

cat("Outlier capping applied to 'avg_glucose_level' and 'bmi'.\n")
```

## Step 5 — Encode Categorical Variables

```{r preprocess-encoding, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Encode categorical variables as factors
# Then convert to numeric for model compatibility

cat_cols <- c("gender", "ever_married", "work_type", "Residence_type", "smoking_status")

stroke_df[cat_cols] <- lapply(stroke_df[cat_cols], as.factor)

# Encode target variable as factor with readable levels
stroke_df$stroke <- factor(stroke_df$stroke,
                            levels = c(0, 1),
                            labels = c("No_Stroke", "Stroke"))

cat("Categorical variables encoded as factors.\n")
cat("Target variable levels:", levels(stroke_df$stroke), "\n")
```

## Step 6 — Feature Engineering

```{r preprocess-feature-engineering, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING (FEATURE ENGINEERING):
# Create new meaningful features to boost model performance

# 1. Age group
stroke_df$age_group <- cut(stroke_df$age,
  breaks = c(0, 18, 40, 60, Inf),
  labels = c("Child", "Young", "Middle_Aged", "Senior"),
  right  = FALSE
)

# 2. Glucose risk category
stroke_df$glucose_risk <- cut(stroke_df$avg_glucose_level,
  breaks = c(0, 100, 126, Inf),
  labels = c("Normal", "Pre_Diabetic", "Diabetic"),
  right  = FALSE
)

# 3. BMI category
stroke_df$bmi_category <- cut(stroke_df$bmi,
  breaks = c(0, 18.5, 24.9, 29.9, Inf),
  labels = c("Underweight", "Normal", "Overweight", "Obese"),
  right  = FALSE
)

# 4. Comorbidity score — sum of hypertension and heart_disease
stroke_df$comorbidity_score <- stroke_df$hypertension + stroke_df$heart_disease

cat("Feature engineering complete. New features: age_group, glucose_risk, bmi_category, comorbidity_score\n")
cat("Total features after engineering:", ncol(stroke_df) - 1, "(excluding target)\n")
```

## Step 7 — Normalize Numerical Features

```{r preprocess-normalization, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Min-Max normalization for numerical features
# Ensures all features are on [0, 1] scale for SVM and others

normalize <- function(x) {
  rng <- range(x, na.rm = TRUE)
  if (diff(rng) == 0) return(rep(0, length(x)))
  (x - rng[1]) / diff(rng)
}

num_cols_to_scale <- c("age", "avg_glucose_level", "bmi", "comorbidity_score")
stroke_df[num_cols_to_scale] <- lapply(stroke_df[num_cols_to_scale], normalize)

cat("Numerical features normalized to [0, 1]:", paste(num_cols_to_scale, collapse = ", "), "\n")
```

## Step 8 — Reduce Skewness (Log Transform Check)

```{r preprocess-skewness, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# PREPROCESSING: Skewness has already been partially addressed
# via outlier capping and normalization.

skew_check <- sapply(stroke_df[c("avg_glucose_level", "bmi")],
                     function(x) round(e1071::skewness(x), 3))

kable(data.frame(Feature = names(skew_check), Skewness = skew_check),
      row.names = FALSE,
      caption   = "Skewness of Numerical Features After Preprocessing") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
```

## Preprocessed Dataset Preview

```{r preprocess-preview, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

cat("Final dataset dimensions:", nrow(stroke_df), "rows x", ncol(stroke_df), "columns\n\n")
cat("Column types after preprocessing:\n")
str(stroke_df)
```

# Modeling

## Train-Test Split

```{r Train-Test split, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODELING: Stratified 80/20 train-test split

set.seed(42)

train_index <- createDataPartition(stroke_df$stroke, p = 0.80, list = FALSE)
train_data  <- stroke_df[train_index,  ]
test_data   <- stroke_df[-train_index, ]

cat("Training set:", nrow(train_data), "rows\n")
cat("Test set    :", nrow(test_data),  "rows\n")
cat("\nClass distribution in training set:\n")
print(prop.table(table(train_data$stroke)))
cat("\nClass distribution in test set:\n")
print(prop.table(table(test_data$stroke)))
```

## Handling Class Imbalance via ROSE

```{r ROSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

set.seed(42)
train_balanced <- ROSE(stroke ~ ., data = train_data, seed = 42)$data

cat("Balanced training set class distribution:\n")
print(table(train_balanced$stroke))
```

## Cross-Validation Setup

```{r CV, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODELING: 5-fold cross-validation configuration

ctrl <- trainControl(
  method          = "cv",
  number          = 5,
  classProbs      = TRUE,
  summaryFunction = twoClassSummary,
  savePredictions = "final"
)
cat("Cross-validation: 5-fold, with class probabilities enabled.\n")
```

## Helper Function: Evaluation Metrics

```{r Helper-Evaluation Metrics, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODELING: Reusable function to compute Accuracy, Precision,
# Recall, and F1-score from a confusion matrix

compute_metrics <- function(actual, predicted, positive_class = "Stroke") {
  cm     <- confusionMatrix(predicted, actual, positive = positive_class)
  acc    <- cm$overall["Accuracy"]
  prec   <- cm$byClass["Precision"]
  recall <- cm$byClass["Recall"]
  f1     <- cm$byClass["F1"]

  list(
    ConfusionMatrix = cm,
    Metrics = data.frame(
      Metric = c("Accuracy", "Precision", "Recall", "F1-Score"),
      Value  = round(c(acc, prec, recall, f1), 4)
    )
  )
}
```


## Model 1 — Logistic Regression (Baseline)

```{r LR, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODEL 1: Logistic Regression
# Simple, interpretable baseline for binary classification

set.seed(42)
cat("Training Logistic Regression...\n")

model_lr <- train(
  stroke ~ .,
  data      = train_balanced,
  method    = "glm",
  family    = "binomial",
  trControl = ctrl,
  metric    = "ROC"
)

# Predict on test set
pred_lr      <- predict(model_lr, newdata = test_data)
results_lr   <- compute_metrics(test_data$stroke, pred_lr)

cat("\nLogistic Regression — Test Set Performance:\n")
print(results_lr$ConfusionMatrix$table)
print(results_lr$Metrics)
```

## Model 2 — Random Forest

```{r RF, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODEL 2: Random Forest

set.seed(42)
cat("Training Random Forest (this may take a moment)...\n")

rf_grid <- expand.grid(mtry = c(3, 5, 7))

model_rf <- train(
  stroke ~ .,
  data      = train_balanced,
  method    = "rf",
  trControl = ctrl,
  tuneGrid  = rf_grid,
  ntree     = 200,
  metric    = "ROC"
)

# Predict on test set
pred_rf    <- predict(model_rf, newdata = test_data)
results_rf <- compute_metrics(test_data$stroke, pred_rf)

cat("\nRandom Forest — Best mtry:", model_rf$bestTune$mtry, "\n")
cat("Random Forest — Test Set Performance:\n")
print(results_rf$ConfusionMatrix$table)
print(results_rf$Metrics)
```

### Random Forest: Feature Importance

```{r RF-Feature Importance, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#Variable importance from Random Forest
# Shows which features most influence stroke prediction

importance_df <- varImp(model_rf)$importance %>%
  rownames_to_column("Feature") %>%
  arrange(desc(Overall)) %>%
  head(15)

ggplot(importance_df, aes(x = reorder(Feature, Overall), y = Overall,
                           fill = Overall)) +
  geom_bar(stat = "identity", width = 0.7) +
  scale_fill_gradient(low = "#90CAF9", high = "#0D47A1") +
  coord_flip() +
  labs(title = "Random Forest: Top 15 Feature Importances",
       x     = "Feature",
       y     = "Importance Score") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "none")
```


## Model 3 — Support Vector Machine (SVM)

```{r SVM, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# MODEL 3: Support Vector Machine

set.seed(42)
cat("Training Support Vector Machine...\n")

svm_grid <- expand.grid(C = c(0.5, 1, 2), sigma = c(0.01, 0.05))

model_svm <- train(
  stroke ~ .,
  data      = train_balanced,
  method    = "svmRadial",
  trControl = ctrl,
  tuneGrid  = svm_grid,
  metric    = "ROC"
)

# Predict on test set
pred_svm    <- predict(model_svm, newdata = test_data)
results_svm <- compute_metrics(test_data$stroke, pred_svm)

cat("\nSVM — Best Parameters: C =", model_svm$bestTune$C,
    ", sigma =", model_svm$bestTune$sigma, "\n")
cat("SVM — Test Set Performance:\n")
print(results_svm$ConfusionMatrix$table)
print(results_svm$Metrics)
```


## 1. Comparative Metrics Table
```{r Comparative Analysis, message=FALSE, warning=FALSE}

comparison_table <- data.frame(
  Model     = c("Logistic Regression", "Random Forest", "SVM (Radial)"),
  Accuracy  = c(
    results_lr$Metrics$Value[1],
    results_rf$Metrics$Value[1],
    results_svm$Metrics$Value[1]
  ),
  Precision = c(
    results_lr$Metrics$Value[2],
    results_rf$Metrics$Value[2],
    results_svm$Metrics$Value[2]
  ),
  Recall    = c(
    results_lr$Metrics$Value[3],
    results_rf$Metrics$Value[3],
    results_svm$Metrics$Value[3]
  ),
  F1_Score  = c(
    results_lr$Metrics$Value[4],
    results_rf$Metrics$Value[4],
    results_svm$Metrics$Value[4]
  )
)

# Show in HTML
knitr::kable(comparison_table, caption = "Model Comparison Table")

# Open in separate tab (Viewer)
View(comparison_table)
```

## 2. ROC Curve - Probability Computation
```{r ROC}

# Convert target properly
true_labels <- ifelse(test_data$stroke == "Stroke", 1, 0)

prob_lr  <- predict(model_lr,  test_data, type = "prob")[, "Stroke"]
prob_rf  <- predict(model_rf,  test_data, type = "prob")[, "Stroke"]
prob_svm <- predict(model_svm, test_data, type = "prob")[, "Stroke"]

roc_lr  <- pROC::roc(true_labels, prob_lr)
roc_rf  <- pROC::roc(true_labels, prob_rf)
roc_svm <- pROC::roc(true_labels, prob_svm)
```

## 3. ROC Dataframe Binding
```{r ROC Plot}

build_roc_df <- function(roc_obj, model_name){
  data.frame(
    TPR = roc_obj$sensitivities,
    FPR = 1 - roc_obj$specificities,
    Model = model_name
  )
}

roc_df <- dplyr::bind_rows(
  build_roc_df(roc_lr,  "Logistic Regression"),
  build_roc_df(roc_rf,  "Random Forest"),
  build_roc_df(roc_svm, "SVM")
)

ggplot(roc_df, aes(x = FPR, y = TPR, color = Model)) +
  geom_line(size = 1.2) +
  scale_color_manual(values = c("#1976D2", "#388E3C", "#F57C00")) +
  geom_abline(linetype = "dashed") +
  labs(title = "ROC Curve Comparison",
       x = "False Positive Rate",
       y = "True Positive Rate") +
  theme_minimal()
```

## 4. Confusion Matrix Visualization
```{r Confusion Matrix}

plot_cm <- function(actual, predicted, title){
  cm <- table(actual, predicted)
  df <- as.data.frame(cm)
  
  ggplot(df, aes(x = predicted, y = actual, fill = Freq)) +
    geom_tile() +
    geom_text(aes(label = Freq), color = "white", size = 5) +
    labs(title = title, x = "Predicted", y = "Actual") +
    theme_minimal()
}

cm1 <- plot_cm(test_data$stroke, pred_lr,  "Logistic Regression")
cm2 <- plot_cm(test_data$stroke, pred_rf,  "Random Forest")
cm3 <- plot_cm(test_data$stroke, pred_svm, "SVM (Radial)")

gridExtra::grid.arrange(cm1, cm2, cm3, ncol = 3)
```

## 5. AUC Summary Table
```{r AUC Table}

auc_df <- data.frame(
  Model = c("Logistic Regression", "Random Forest", "SVM (Radial)"),
  AUC   = round(c(pROC::auc(roc_lr), pROC::auc(roc_rf), pROC::auc(roc_svm)), 4)
)

knitr::kable(auc_df, caption = "AUC Comparison")
View(auc_df)
```